---
title: "RBFCCF Quick Stats"
author: "Jzushi"
date: "9/6/2019"
output: html_document
---
```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# RBFCCF Quick Stats

### Included in this sheet are the variables we tested, brief coding and stats, as well as simple graphs.



## Fitness Level ~ MARCI

```{r, warning=FALSE, include=FALSE }
library(tidyverse)
library(modelr)
library(ggplot2)
library(lme4)
library(emmeans)
library(tinytex)


df <- read.csv("../Sawyer_Research_Data_Analysis/MetaData_exc.csv", stringsAsFactors = FALSE)
names(df)
glimpse(df)

# Separate the sex
MaleT<- grep("^M", df$Sex)
FemaleT<- grep("^F", df$Sex)


# Remove Controls and blanks from group 
df <- subset(df, Sex != "")
df <- subset(df, Subject != "NA")
df <- subset(df, MARCI != "NA")
df <- subset(df, Fitness_Level != "NA")



Runs <- subset(df, Group != "Control")
glimpse(Runs)

# Change categories
Runs$Fitness_Level <- as.factor(Runs$Fitness_Level)
Runs$MARCI <- as.numeric(Runs$MARCI)

```

### Quick Plot 
Fitness Level ~ MARCI

```{r, warning=FALSE }
MARCIPlot <- ggplot(data = Runs, aes(x = Fitness_Level, y = MARCI)) +
  geom_bar(stat="identity")
MARCIPlot
```

### Modeling

```{r, warning=FALSE }
RunsMarci = lm(MARCI ~ Fitness_Level, data = Runs)
summary(RunsMarci)
``` 

### Checking Validity

```{r, warning=FALSE}
# Residuals 
epsMarci <- residuals(RunsMarci) 
qqnorm(epsMarci) 
qqline(epsMarci) 

# Homoscedasticity 
yhatMarci <- fitted(RunsMarci) 
plot(yhatMarci,epsMarci) 
abline(h=0) 

```




## Fitness Level ~ Spatial Reasoning

```{r, warning=FALSE, include=FALSE }
library(tidyverse)
library(modelr)
library(ggplot2)
library(lme4)
df <- read.csv("../Sawyer_Research_Data_Analysis/MetaData_exc.csv", stringsAsFactors = FALSE)
names(df)
glimpse(df)

# Separate the sex
MaleT<- grep("^M", df$Sex)
FemaleT<- grep("^F", df$Sex)


# Remove Controls and blanks from group 
df <- subset(df, Sex != "")
df <- subset(df, Subject != "NA")
df <- subset(df, Spatial_reasoning_time != "NA")
## Remove Spatial NA
Runs <- subset(df, Group != "Control")
glimpse(Runs)

# Change categories
Runs$Fitness_Level <- as.factor(Runs$Fitness_Level)
Runs$Spatial_reasoning_score <- as.numeric(Runs$Spatial_reasoning_score)
Runs$Spatial_reasoning_time <- as.numeric(Runs$Spatial_reasoning_time)
```

### Quick Plot 
Fitness Level ~ Spatial Reasoning Score

```{r, warning=FALSE }
Spatial_Score_Plot <- ggplot(data = Runs, aes(x = Fitness_Level, y = Spatial_reasoning_score)) +
  geom_bar(stat="identity")
Spatial_Score_Plot
```

Fitness Level ~ Spatial Reasoning Time

```{r, warning=FALSE}
Spatial_Time_Plot <- ggplot(data = Runs, aes(x = Fitness_Level, y = Spatial_reasoning_time)) +
  geom_bar(stat="identity")
Spatial_Time_Plot
```

### Modeling

```{r, warning=FALSE }
RunsSpatial = lm(Spatial_reasoning_time + Spatial_reasoning_score ~ Fitness_Level, data = Runs)
summary(RunsSpatial)
``` 

### Checking Validity

```{r, warning=FALSE}
# Residuals 
epsSpatial <- residuals(RunsSpatial) 
qqnorm(epsSpatial) 
qqline(epsSpatial) 

# Homoscedasticity 
yhatSpatial <- fitted(RunsSpatial) 
plot(yhatSpatial,epsSpatial) 
abline(h=0) 
```


## Fitness Level ~ Pre Stroop Tests

```{r, warning=FALSE, include=FALSE }
library(tidyverse)
library(modelr)
library(ggplot2)
library(lme4)
df <- read.csv("../Sawyer_Research_Data_Analysis/MetaData_exc.csv", stringsAsFactors = FALSE)
names(df)
glimpse(df)

# Separate the sex
MaleT<- grep("^M", df$Sex)
FemaleT<- grep("^F", df$Sex)


# Remove Controls and blanks from group 
df <- subset(df, Sex != "")
df <- subset(df, Subject != "NA")
Runs <- subset(df, Group != "Control")
glimpse(Runs)

# Change categories
Runs$Fitness_Level <- as.factor(Runs$Fitness_Level)
Runs$Pre_stroop1 <- as.numeric(Runs$Pre_stroop1)
Runs$Pre_stroop2 <- as.numeric(Runs$Pre_stroop2)

```

### Quick Plot 
Fitness Level ~ Pre Stroop Condition 1

```{r, warning=FALSE }
Fit_Pre_Stroop1_Plot <- ggplot(data = Runs, aes(x = Fitness_Level, y = Pre_stroop1)) +
  geom_bar(stat="identity")
Fit_Pre_Stroop1_Plot
```

Fitness Level ~ Pre Stroop Condition 2

```{r, warning=FALSE}
Fit_Pre_Stroop2_Plot <- ggplot(data = Runs, aes(x = Fitness_Level, y = Pre_stroop2)) +
  geom_bar(stat="identity")
Fit_Pre_Stroop2_Plot

```

### Modeling

```{r, warning=FALSE }
Runs_Pre_Stroop = lm(Pre_stroop1 + Pre_stroop2 ~ Fitness_Level, data = Runs)
summary(Runs_Pre_Stroop)
``` 

### Checking Validity

```{r, warning=FALSE}
# Residuals 
# Residuals 
epsPreStroop <- residuals(Runs_Pre_Stroop) 
qqnorm(epsPreStroop) 
qqline(epsPreStroop) 

# Homoscedasticity 
yhatPreStroop <- fitted(Runs_Pre_Stroop) 
plot(yhatPreStroop,epsPreStroop) 
abline(h=0) 
```

## Fitness Level ~ ABC

```{r, warning=FALSE, include=FALSE }
library(tidyverse)
library(modelr)
library(ggplot2)
library(lme4)
df <- read.csv("../Sawyer_Research_Data_Analysis/MetaData_exc.csv", stringsAsFactors = FALSE)
names(df)
glimpse(df)

# Separate the sex
MaleT<- grep("^M", df$Sex)
FemaleT<- grep("^F", df$Sex)


# Remove Controls and blanks from group 
df <- subset(df, Sex != "")
df <- subset(df, Subject != "NA")
Runs <- subset(df, Group != "Control")
glimpse(Runs)

# Change categories
Runs$Fitness_Level <- as.factor(Runs$Fitness_Level)
Runs$ABC <- as.numeric(Runs$ABC)
```

### Quick Plot 
Fitness Level ~ ABC

```{r, warning=FALSE }
ABCPlot <- ggplot(data = Runs, aes(x = Fitness_Level, y = ABC)) +
  geom_bar(stat="identity")
ABCPlot
```

### Modeling
```{r, warning=FALSE }
RunsABC = lm(ABC ~ Fitness_Level, data = Runs)
summary(RunsABC)
``` 

### Checking Validity
```{r, warning=FALSE}
# Residuals 
epsABC <- residuals(RunsABC) 
qqnorm(epsABC) 
qqline(epsABC) 

# Homoscedasticity 
yhatABC <- fitted(RunsABC) 
plot(yhatABC,epsABC) 
abline(h=0) 
```

## Fitness Level ~ ILP

```{r, warning=FALSE, include=FALSE }
library(tidyverse)
library(modelr)
library(ggplot2)
library(lme4)
df <- read.csv("../Sawyer_Research_Data_Analysis/MetaData_exc.csv", stringsAsFactors = FALSE)
names(df)
glimpse(df)

# Separate the sex
MaleT<- grep("^M", df$Sex)
FemaleT<- grep("^F", df$Sex)


# Remove Controls and blanks from group 
df <- subset(df, Sex != "")
df <- subset(df, Subject != "NA")
Runs <- subset(df, Group != "Control")
glimpse(Runs)

# Change categories
Runs$Fitness_Level <- as.factor(Runs$Fitness_Level)
Runs$ILP_Speaking <- as.numeric(Runs$ILP_Speaking)
Runs$ILP_Reading_and_writing <- as.numeric(Runs$ILP_Reading_and_writing)
Runs$ILP_time_management <- as.numeric(Runs$ILP_time_management)
```

### Quick Plot 
Fitness Level ~ ILP Speaking

```{r, warning=FALSE }
SpeakingPlot <- ggplot(data = Runs, aes(x = Fitness_Level, y = ILP_Speaking)) +
  geom_bar(stat="identity")
SpeakingPlot

```

Fitness Level ~ ILP Reading and Writing

```{r, warning=FALSE }
ReadingPlot <- ggplot(data = Runs, aes(x = Fitness_Level, y = ILP_Reading_and_writing)) +
  geom_bar(stat="identity")
ReadingPlot
```

Fitness Level ~ ILP Time Management

```{r, warning=FALSE }
ManagementPlot <- ggplot(data = Runs, aes(x = Fitness_Level, y = ILP_time_management)) +
  geom_bar(stat="identity")
ManagementPlot
```

### Modeling
```{r, warning=FALSE }
RunsILP = lm(ILP_Speaking + ILP_Reading_and_writing + ILP_time_management ~ Fitness_Level, data = Runs)
summary(RunsILP)
``` 

### Checking Validity
```{r, warning=FALSE}
# Residuals 
epsILP <- residuals(RunsILP) 
qqnorm(epsILP) 
qqline(epsILP) 

# Homoscedasticity 
yhatILP <- fitted(RunsILP) 
plot(yhatILP,epsILP) 
abline(h=0) 
```
